Log Journal Project Theme 9

### 2022-10-14 Resources/LogJournal.Rmd
Added barplot in the MIL Section (Did not knit)

```{r}
wekaResult <- read.table("ResultWeka.txt", header = TRUE)
colnames(wekaResult) <- c("Classifier", "TP Rate Avg.", "FP Rate Avg.", 
                          "Precision", "VAC Precision")
pander(wekaResult)
```

Several algorithms cannot make a prediction for the classification VAC (0.000) and for some they get an error (?). 1 algorithm IBk has a very low prediction for VAC. All the algorithm above in table NUMBER except for ZeroR, OneR, SMO and SimpleLogistic were used in the Weka Experimenter to compare.

@@

Since there are 10 classifications, ROC curve have been caught from one classifications.

![ROC Curve (NUC)]("images/ROCCurve.png")

This is a nice curve with a relative low ROC Curve. This means that this classification can correspond well to a particular decision threshold.

>>>>

The experimenter can save the results in a csv file.

```{r}
weka.result <- read.table("Result.csv", header = TRUE, sep = ",")
# Remove weka.classifiers.* from classifier name
for (i in 1:length(weka.result$Key_Scheme)) {
  name <- weka.result$Key_Scheme[i]
  tweaked.name <- strsplit(name, split = ".", fixed = TRUE)[[1]][4]
  weka.result$Key_Scheme[i] <- tweaked.name
}
```

Now the results of the csv can been plotted with ease of use. Like the ROC and precision.

```{r, fig.cap="Area under the curve for different classifiers"}
# Create a dataframe of the mean of the ROC of every classifier
res <- aggregate(Area_under_ROC ~ Key_Scheme, data = weka.result, mean)

ggplot(data=res, aes(x=Key_Scheme, y=Area_under_ROC, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + 
  labs(x="Classifier", y="Area under curve (ROC)", 
       title="Area under the curve for different classifiers") + 
  geom_hline(aes(yintercept=min(Area_under_ROC)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(Area_under_ROC)), linetype = 'dashed') + 
  geom_text(aes(label=round(Area_under_ROC, digits=2)), vjust=-0.3, size=3.5)
```

RandomForest has the highest area under the curve, while OneR has the lowest with 0.49 and ZeroR with a close second last with 0.5.

```{r, fig.cap="Average precisionfor different classifiers"}
res <- aggregate(IR_precision ~ Key_Scheme, data = weka.result, mean)

ggplot(data=res, aes(x=Key_Scheme, y=IR_precision, fill=Key_Scheme)) + 
  geom_bar(stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + 
  labs(x="Classifier", y="Precision", 
       title="Average precisionfor different classifiers") + 
  geom_hline(aes(yintercept=min(IR_precision)), linetype = 'dashed') + 
  geom_hline(aes(yintercept=max(IR_precision)), linetype = 'dashed') + 
  geom_text(aes(label=round(IR_precision, digits=2)), vjust=-0.3, size=3.5)
```

RandomForest also has the highest average precision with 0.66. And OneR has the lowest with 0.04. ZeroR is not in this plots because it only consist of NaN.

Several algorithms cannot make a prediction for the classification VAC (0.000) and for some they get an error (?). 1 algorithm IBk has a very low prediction for VAC. All the algorithm above in the figure except for ZeroR, OneR, SMO and SimpleLogistic were used in the Weka Experimenter to compare.

@@
